Effects of the body force on the evacuation dynamics

### 2019-11-26 paper.tex
incorporacion de mas graficos

>>>>

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_density7_width22_kn0.eps}\label{flow_density_nocomp}}\ 
    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_density7_width22_knE5.eps}\label{flow_density_comp}}\\
        \subfloat[]{\includegraphics[width=0.40\columnwidth]{./tesselation_d7_t30_kn0.eps}\label{tesselation_d7_t30_kn0}}\
    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./tesselation_d7_t30_knE5.eps}\label{tesselation_d7_t30_knE5}}\\
            \subfloat[]{\includegraphics[width=0.40\columnwidth]{./g(r)_d7_kn0.eps}\label{g(r)_d7_kn0}}\
    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./g(r)_d7_knE5.eps}\label{g(r)_d7_knE5}}\\
\caption[width=0.47\columnwidth]{}
\label{flow_density}
\end{figure}

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./triangles.eps}
\caption{\label{} }
\end{figure}
